Complexity analysis and a fully polynomial-time approximation scheme for the college application problem

### 2022-07-01 paper/paper.tex
two paragraphs about the Pandora's Box problem

\subsection{Literature review}

@@

To the best of our knowledge, the first systematic study of the college application p·roblem was conducted by this article's first author in his master's thesis (Kapur 2022). A special case of \eqref{headlineproblem} arose in an equilibrium analysis of the United States college admissions market by Fu (2014). However, her econometric task involved clustering the schools such that $m=8$, a scale at which enumeration is tractable. We are interested in solution techniques that scale efficiently in the number of colleges. The present article extends Kapur's key results with a more precise analysis of the problem's computational complexity and a new solution algorithm.

>>>>

\subsection{Literature review}
One way of thinking about the college application problem is as a static variant of the Pandora's Box problem proposed by Weitzman (1979). In a Pandora's Box formulation of college application, the student applies to schools one by one, each time paying the application fee and observing her admissions outcome after a time delay. The problem is to determine an optimal \emph{stopping policy} for when Pandora should halt her college search and accept the best admissions offer she has on hand. Weitzman showed that the optimal policy is to halt the search when the difference between the value of current best offer and the maximum \emph{reservation price,} a statistic over the set of colleges to which Pandora has not yet applied, is positive.

Arguably, the static model considered in this study is more hostile to students than the Pandora's Box problem. If, for example, an unlucky Pandora is rejected from a safety school at an early round of application, then she can pivot to a more risk-averse application strategy. By contrast, the decisionmaker in our college application problem must commit to her entire application portfolio at the outset. The admissions process used in the United States can be viewed as the concatenation of both problems: In the fall, students solve \eqref{headlineproblem} and send out a batch of applications. Then, upon observing their admissions outcomes in March, they use the Pandora strategy to pursue additional offers by applying in the spring and summer to schools that offer rolling admissions.

@@

To the best of our knowledge, the first systematic study of the college application problem was conducted by this article's first author in his master's thesis (Kapur 2022). A special case of \eqref{headlineproblem} arose in an equilibrium analysis of the United States college admissions market by Fu (2014). However, her econometric task involved clustering the schools such that $m=8$, a scale at which enumeration is tractable. We are interested in solution techniques that scale efficiently in the number of colleges. The present article extends Kapur's key results with a more precise analysis of the problem's computational complexity and a new solution algorithm.
